Scalar Parametrization for Joint Time-Frequency interpolation in a MIMO-OFDM channel

### 2019-10-09 paper/main.tex
modified adpm figure and added changes to main.tex

\begin{equation} 
y_{i,t} = H_{i,t} x_{i,t}+ \eta 
\end{equation}

@@

where the channel matrix $H_{i,t} \in \mathbb{C}^{N_R \times N_T}$; the input $x_{i,t} \in \mathbb{C}^{N_T}$; the output $y_{i,t} \in \mathbb{C}^{N_R}$ and $\eta$ is the complex additive white gaussian noise vector with distribution $\tilde{\mathcal{N}}(0,I_{N_R})$. On applying thin SVD to H, we get $H_{i,t} = U_{i,t} \Sigma_{i,t} V_{i,t}^{H}$, where $U_{i,t} \in \mathbb{C}^{N_R \times N_T}$, $\Sigma_{i,t} \in \mathbb{C}^{N_T \times N_T}$  and $V_{i,t} \in \mathbb{C}^{N_T \times N_T}$. $U_{i,t}$ and $V_{i,t}$ are orthonormal column matrices and $\Sigma_{i,t}$ contains the singular values $\sigma_1 \geq \ldots \geq \sigma_{N_T} > 0$ of H. The entries of H are assumed to be i.i.d. $\tilde{\mathcal{N}}(0,1)$, complex circularly symmetric Gaussian with mean zero and variance 1. Therefore, the first n column vectors of $V_{i,t}$ have to be quantized and fed back to the transmitter as channel spatial information.

% Givens rotation definition and how we are decomposing, Theta- pdf = 2lsin(theta)(2l-1).cos(theta) 0 $\leq$ Theta $\leq$ pi/2. 
% Householders' transformation and how we are decomposing. -pi$\leq$ phi $\leq$ pi. Uniformly distributed. 
% Low-complexity quantization scheme based on a further parameterization of a vector in 
% terms of a minimal number of independent scalar parameters. In particular, we consider its application to CSI feedback in slowly time-varying MIMO channels

@@

I_{m-2} & & & \\ 
& cos\;\theta & - sin\;\theta & \\ 
& sin\;\theta & cos\;\theta & \\ 
& & & I_{t-m}

@@

\begin{figure} 
\includegraphics[width=0.5\textwidth]{images/adpm.pdf} 
\caption{Subcarriers which need to be quantized} 
\label{ber_overvie}
\vspace{-5pt} 
\end{figure}

@@

\begin{equation} 
p(\theta) = 2lsin(\theta)^{2l-1}cos(\theta), \theta \in [0, \frac{\pi}{2}), for \; l = 1,2,\ldots,t-1
\end{equation}

@@

One problem associated with the tracking of phases ($\phi$) is that they change abruptly (cite the figure) between $-\pi$ and $\pi$ since $sin/cos(\pi) = sin/cos(-\pi)$. Therefore we have to wrap around the values by removing those abrupt changes (/cite another figure here).

@@

Now here we can see the advantage of using subcarriers in an alternating fashion as given in the previous section. With this method we could exploit both time and frequency correlation because

@@

\subsection{Initial Quantization} 
For the first and the second simulations/time instances we use of $\textbf{B}$ = 10 bits for quantizing each parameter for effective quantization/initialization. Therefore, the number of bits for each subcarrier = $10\times12$ = 120. Quantization is performed as given in \ref{section2}.

>>>>

\begin{equation} 
\by_{i,t} = \bH_{i,t} \bx_{i,t}+ \bf{\eta_{i,t}} 
\end{equation}

@@

where the channel matrix $\bH_{i,t} \in \mathbb{C}^{N_R \times N_T}$; the input $\bx_{i,t} \in \mathbb{C}^{N_T}$; the output $\by_{i,t} \in \mathbb{C}^{N_R}$ and $\eta$ is the complex additive white gaussian noise vector with distribution $\tilde{\mathcal{N}}(0,I_{N_R})$. On applying thin SVD to H, we get $\bH_{i,t} = U_{i,t} \Sigma_{i,t} V_{i,t}^{H}$, where $U_{i,t} \in \mathbb{C}^{N_R \times N_R}$, $\Sigma_{i,t} \in \mathbb{C}^{N_R \times N_R}$  and $V_{i,t} \in \mathbb{C}^{N_T \times N_R}$. $U_{i,t}$ and $V_{i,t}$ are orthonormal column matrices and $\Sigma_{i,t}$ contains the singular values $\sigma_1 \geq \ldots \geq \sigma_{N_T} > 0$ of H. The entries of H are assumed to be i.i.d. $\tilde{\mathcal{N}}(0,1)$, complex circularly symmetric Gaussian with mean zero and variance 1. Therefore, the first n column vectors of $V_{i,t}$ have to be quantized and fed back to the transmitter as channel spatial information.

% Givens rotation definition and how we are decomposing, Theta- pdf = 2lsin(theta)(2l-1).\cos(theta) 0 $\leq$ Theta $\leq$ pi/2. 
% Householders' transformation and how we are decomposing. -pi$\leq$ phi $\leq$ pi. Uniformly distributed. 
% Low-complexity quantization scheme based on a further parameterization of a vector in 
% terms of a minimal number of independent scalar parameters. In particular, we consider its application to CSI feedback in slowly time-varying MIMO channels

@@

I_{m-2} & & & \\ 
& \cos\;\theta & - \sin\;\theta & \\ 
& \sin\;\theta & \cos\;\theta & \\ 
& & & I_{t-m}

@@

\begin{figure} 
\includegraphics[width=0.45\textwidth]{images/new-adpm-crop.pdf} 
\caption{Subcarriers which need to be quantized} 
\label{ber_overvie}
\vspace{-5pt} 
\end{figure}

@@

\begin{equation} 
p(\theta) = 2l\sin(\theta)^{2l-1}\cos(\theta), \theta \in [0, \frac{\pi}{2}), for \; l = 1,2,\ldots,t-1
\end{equation}

@@

One problem associated with the tracking of phases ($\phi$) is that they change abruptly (cite the figure) between $-\pi$ and $\pi$ since $\sin/\cos(\pi) =\sin/\cos(-\pi)$. Therefore we have to wrap around the values by removing those abrupt changes (/cite another figure here).

@@

Now here we can see the advantage of using subcarriers in an alternating fashion as given in the Section~\ref{section1}. With this method we could exploit both time and frequency correlation because

@@

\subsection{Initial Quantization} 
For the first and the second simulations/time instances we use of $\textbf{B}$ = 10 bits for quantizing each parameter for effective quantization/initialization. Therefore, the number of bits for each subcarrier = $10\times12$ = 120. Quantization is performed as given in Section~\ref{section2}.
